---
title: "linear model from Web"
author: "Nikki Gordon"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

```{r}
predictionpts<-data.frame(ARM=88, GRIP=94) 
predictionpts
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS


### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point(aes(col=ARM)) 
```

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

#### Predict at target point
```{r}
new<-data.frame(ARM=88,GRIP=94)
predict(model.1,new)
```



#### scatterplot with model fit
```{r}
basicNN + geom_point(aes(col=SIMS)) + geom_smooth(method=lm)
```   



## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
plot(SIMS~GRIP,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point(aes(col=GRIP)) 
```

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

#### predict model.2 at target point
```{r}
new<-data.frame(ARM=88,GRIP=94)
predict(model.2,new)
```
#### now add the model fit to our plot for model.2
```{r}
basicNN + geom_point(aes(col=GRIP)) + geom_smooth(method=lm)
```     


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)


  
### Inferential  (Build 2-dimentional model.3)

````{r}
advNN <- ggplot(data,aes(y=SIMS,x=ARM,z=GRIP))
```
```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
``` 

#### predict model.3 at target point
```{r}
new<-data.frame(ARM=88,GRIP=94)
predict(model.3,new)
```  

## Comparing nested models ANOVA Test
```{r}
anova(model.1,model.2)
anova(model.2,model.3)
anova(model.1,model.3)
```
### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

